---
title: "Activity: Simple Linear Regression"
subtitle: "Height vs. Shoe Size"
---


## **Objective**

You will:

- Identify predictor (height) and response (shoe size).
- Explain what the slope means in context.
- Recognize variability and limitations of small-sample regressions.
- Experience how combining data strengthens inference.


## Instructions

(1) Form a group of 4 or 5. (This is your sample size!)

(2) Collect your data. Each person will share their **height** and **shoe size**! 
    - Height ($X$): **inches** (Use [feet-to-inch conversion](https://www.rapidtables.com/convert/length/feet-inch-to-inch.html) to help you get your height in inches.)
    - Shoe Size ($Y$): **US**
  
(3) Make a R data frame. (Replace my numbers with your data!)

```{r}
df <- data.frame(height = c(69, 74, 77, 60, 62), 
                 size = c(11, 10.5, 12, 9.5, 9))
df
```


(4) Analyze within your group.

```{r}
#| eval: false
# (a) Plot your data. Height on the x-axis, Shoe Size on the y-axis.
plot(x = ______, y = _______)
```


```{r}
#| eval: false
# (b) Fit the simple linear regression model
model <- lm(____ ~ ____)

# (c) Draw the fitted regression line.
abline(______)
```


```{r}
#| eval: false

# (d) Obtain the estimated slope. What does it mean in context? Is the effect statistically significant?
```


## Discussion

- How does your group’s pattern compare to the overall line?
- What does the slope mean in context?
- Why might individual data vary around the line?
- Would it make sense to predict shoe size for someone far outside our data range (e.g., 7'3" tall)? Why or why not?
